Path Model Temperature Comparisons

### 2019-04-07 path-temp-compare.Rmd
Analyse SAC

```{r test SAC diversity model residuals, echo=F}
library(spBayes); library(classInt); library(RColorBrewer); library(geoR)
summary(na.omit(oakplots.2006))
points <- select(na.omit(oakplots.2006), X, Y)
points <- as.matrix(dist(cbind(points$X, points$Y)))
points.inv <- 1/points
diag(points.inv) <- 0
shannons.resids <- resid(shannons)
max.dist <- 0.33 * max(iDist(points))
bins <- 100

vario.shannons <- variog(coords = points, 
                     data = na.omit(oakplots.2006$shannons2005.scl),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.shannons <- variofit(
      vario.shannons,
      ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.shannons)
lines(fit.vario.shannons)
abline(h = fit.vario.shannons$nugget, col = "blue")# nugget
abline(h = fit.vario.shannons$cov.pars[1] + fit.vario.shannons$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.shannons$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario.umca_density <- variog(coords = points_rep, 
                     data = na.omit(umca_density@frame$tot_bay.log),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density <- variofit(
      vario.umca_density,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.umca_density)
lines(fit.vario.umca_density)
abline(h = fit.vario.umca_density$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density$cov.pars[1] + fit.vario.umca_density$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario.slc <- variog(coords = points_rep, 
                     data = na.omit(slc@frame$tot_lfct.log),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.slc <- variofit(
      vario.slc,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.slc)
lines(fit.vario.slc)
abline(h = fit.vario.slc$nugget, col = "blue")# nugget
abline(h = fit.vario.slc$cov.pars[1] + fit.vario.slc$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.slc$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario. <- variog(coords = points_rep, 
                     data = na.omit(umca_density@frame$tot_bay.log),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density <- variofit(
      vario.umca_density,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.umca_density)
lines(fit.vario.umca_density)
abline(h = fit.vario.umca_density$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density$cov.pars[1] + fit.vario.umca_density$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density$cov.pars[2], col = "red3")# range

vario.umca_density.resids <- variog(coords = points_rep,
                               data = umca_density.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density.resids <- variofit(
      vario.umca_density.resids,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
# par(mfrow = c(1,2))
plot(vario.umca_density.resids, 
     main = "Variogram - UMCA deensity model residuals",
     xlab = "distance (m)")
lines(fit.vario.umca_density.resids)
abline(h = fit.vario.umca_density.resids$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density.resids$cov.pars[1] + fit.vario.umca_density.resids$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density.resids$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(dist(cbind(points_rep$x, points_rep$y)))
points_rep.inv <- 1/points_rep
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

Moran.I(oak_infection.resids, points_rep.inv)
```

>>>>

```{r test SAC diversity model residuals, echo=F}
library(spBayes); library(classInt); library(RColorBrewer); library(geoR)
summary(na.omit(as.data.frame(oakplots.2006)))
points <- select(na.omit(as.data.frame(oakplots.2006)), X, Y)
points <- as.matrix((cbind(points$X, points$Y)))
points.inv <- 1/(iDist(points))
diag(points.inv) <- 0
shannons.resids <- resid(shannons)
max.dist <- 0.33 * max(iDist(points))
bins <- 100

vario.shannons <- variog(coords = points, 
                     data = na.omit(oakplots.2006$shannons2005.scl),
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.shannons <- variofit(
      vario.shannons,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.shannons)
lines(fit.vario.shannons)
abline(h = fit.vario.shannons$nugget, col = "blue")# nugget
abline(h = fit.vario.shannons$cov.pars[1] + fit.vario.shannons$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.shannons$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- as.matrix(cbind(points_rep$x, points_rep$y))
points_rep.inv <- 1/(iDist(points_rep))
points_rep.inv[points_rep.inv=="Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario.umca_density <- variog(coords = points_rep, 
                     data = umca_density@frame$umca_density_ha.log.scl,
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.umca_density <- variofit(
      vario.umca_density,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.umca_density)
lines(fit.vario.umca_density)
abline(h = fit.vario.umca_density$nugget, col = "blue")# nugget
abline(h = fit.vario.umca_density$cov.pars[1] + fit.vario.umca_density$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.umca_density$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- cbind(points_rep$x, points_rep$y)
points_rep.inv <- 1/iDist(points_rep)
points_rep.inv[points_rep.inv == "Inf"] <- 0
str(points_rep.inv)

# Plot variograms
vario.slc <- variog(coords = points_rep, 
                     data = slc@frame$tot_lfct.log,
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.slc <- variofit(
      vario.slc,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario.slc)
lines(fit.vario.slc)
abline(h = fit.vario.slc$nugget, col = "blue")# nugget
abline(h = fit.vario.slc$cov.pars[1] + fit.vario.slc$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.slc$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- cbind(points_rep$x, points_rep$y)
points_rep.inv <- 1/iDist(points_rep)
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

# Plot variograms
vario <- variog(coords = points_rep, 
                     data = wet_hours_1422@frame$avg_hrs1422_wet_t_t1.log,
                     uvec = (seq(0, max.dist, length = bins)))
fit.vario.wet_hours <- variofit(
      vario,
      # ini.cov.pars = c(300, 200/-log(0.5)),
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
par(mfrow = c(1,2))
plot(vario)
lines(fit.vario.wet_hours)
abline(h = fit.vario.wet_hours$nugget, col = "blue")# nugget
abline(h = fit.vario.wet_hours$cov.pars[1] + fit.vario.wet_hours$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.wet_hours$cov.pars[2], col = "red3")# range

vario.wet_hours.resids <- variog(coords = points_rep,
                               data = wet_hours.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.wet_hours.resids <- variofit(
      vario.wet_hours.resids,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
# par(mfrow = c(1,2))
plot(vario.wet_hours.resids, 
     main = "Variogram - Wet-hours model residuals",
     xlab = "distance (m)")
lines(fit.vario.wet_hours.resids)
abline(h = fit.vario.wet_hours.resids$nugget, col = "blue")# nugget
abline(h = fit.vario.wet_hours.resids$cov.pars[1] + fit.vario.wet_hours.resids$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.wet_hours.resids$cov.pars[2], col = "red3")# range

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- cbind(points_rep$x, points_rep$y)
points_rep.inv <- 1/iDist(points_rep)
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

@@

# all.equal(plots1$plotid,plots2$plotid)
points_rep <- left_join(plots1, plots2, by = c("plotid"="plot_id"))
summary(points_rep)
points_rep <- cbind(points_rep$x, points_rep$y)
points_rep.inv <- 1/iDist(points_rep)
points_rep.inv[points_rep.inv == "Inf"] <- 0
summary(points_rep.inv)

Moran.I(oak_infection.resids, points_rep.inv)

vario.oak_infection.resids <- variog(coords = points_rep,
                               data = oak_infection.resids,
                               uvec = (seq(0, max.dist, length = bins)))
fit.vario.oak_infection.resids <- variofit(
      vario.oak_infection.resids,
      cov.model = "exponential",
      minimisation.function = "optim",
      weights = "equal"
)
# par(mfrow = c(1,2))
plot(vario.oak_infection.resids, 
     main = "Variogram - Wet-hours model residuals",
     xlab = "distance (m)")
lines(fit.vario.oak_infection.resids)
abline(h = fit.vario.oak_infection.resids$nugget, col = "blue")# nugget
abline(h = fit.vario.oak_infection.resids$cov.pars[1] + fit.vario.oak_infection.resids$nugget, col = "green")# sill
abline(v = -log(.05) * fit.vario.oak_infection.resids$cov.pars[2], col = "red3")# range
```
